%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
	{Software Engineering Intern}
	{JPMorgan Chase \& Co.}
	{New York, New York}
	{Jun. 2019 - Aug. 2019}
{								
	\begin{cvitems}
        \item {Built a front-end with \textbf{React} and \textbf{Typescript} to present a Graphical User Interface for Traders in the Algo Trading Team that \textbf{reduced decision time by 40\%}, allowing traders to make more effective and efficient bids}
        \item {Worked in a team to build a back-end using \textbf{Python's Tornado framework} that parses pdf files, saves to JPM’s relational database and sends responses to the frontend using \textbf{RESTful APIs}}
        \item {Wrote code to search, sort, filter, and query old bids to present the closest historical bid}
	\end{cvitems}
}

\cventry
{iOS Instructor}
{Codepath, Org.}
{New York, New York}
{Jan. 2019 - May. 2019}
{
\begin{cvitems}
\item {Taught 40 CUNY students programming in \textbf{Swift, iOS development, Git, UI Design, and Deployment}}
\item {Built \textbf{Twitter, Instagram, and Tumblr clones} and taught students how to build them in class}
\item {Hosted a hackathon \textbf{sponsored by JPMorgan \& Google} where students demonstrated the applications they developed over 4 weeks}
\item {Led the \textbf{largest and most successful cohort} in Codepath\'s history}
\end{cvitems}
}

\cventry
{Remote Software Engineer} % Job title
{Decenture, Inc.} % Organization
{Leeds, UK} % Location
{Jun. 2018 - Aug. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Built and presented a web application, METIS, that resulted in partnerships with CUNY and The New School}
\item {Implemented \textbf{CRUD} functionality using \textbf{MongoDB, Node.js, Express.js, and Heroku}}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Software Engineer Intern} % Job title
{Alice, Inc.} % Organization
{New York, New York} % Location
{Jun. 2017 - Aug. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Utilized \textbf{Slack and Trello API} to build a \textbf{Slackbot} using \textbf{Node.js} that provided daily, weekly, and monthly analysis of the engineering and sales teams’ progress}
\item {Deployed the application on \textbf{Heroku} with timed runs}
\item {Eliminated the need of daily standups for the teams because of the transparency as a result of the new application}
\item {Acted as the \textbf{Scrum Master} of the team with daily standups, and \textbf{Agile project management}}
\end{cvitems}
}

\cvsection{Projects}
%------ CV Entires


\cventry
{iOS Application} % Job title
{Outfit Recommendation Engine Using Live Weather} % Organization
{New York, New York} % Location
{Mar. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Placed in Cooper Hacks as the \textbf{Most Innovative Solution and Best Use of Google Cloud Platform}}
\item {iOS Application that uses \textbf{Yahoo Weather Restful API} to recommend an outfit based on the user's wardrobe and the current weather}
\item {Built the front-end and back-end using \textbf{Swift}, ML using \textbf{Python}, and Database with \textbf{Firebase}}
\end{cvitems}
}

\cventry
{Web Application} % Job title
{Amazon Smile Clone} % Organization
{New York, New York} % Location
{May. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Worked with a partner to build a replica of Amazon Smile using \textbf{PHP, JS, Bootstrap, MySQL, Linux, and Apache (LAMP stack)}}
\item {Implemented \textbf{insertion, searching, sorting, and filtering} of various products}
\item {Built functionality that allows users to pick a charity from the database and automatically donate per purchase}
\end{cvitems}
}

\end{cventries}
